---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `educ7610`


The goal of `educ7610` is to make several aspects of the Regression course (EDUC/PSY 7610) at Utah State University more accessible. Specifically, it provides the data from Darlington and Hayes' book "Regression Analysis and Linear Models", a syntax to perform diagnostics and Johnson-Neyman, odds ratios from logistic regression, among other things. In conjunction with packages like `interactions` and the `easystats` group of packages, this package can make regression analyses more straightforward.

## Installation

You can install the development version from GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("tysonstanley/educ7610")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(educ7610)
data("poverty")  ## load the poverty data set

model <- lm(TeenBirth ~ ViolentCrime + poverty_pct,
           data = poverty)
diagnostics(model) %>% head()
```

